---
title: Homework 1
subtitle: p-values
author: Rahul
date: today
toc: true
---

```{r}
#| message: false
#| echo: false

library(tidyverse)
```

# Section 1: Basic text formatting

## Sub-section


### Header

- some
- words
- in 
- bullets

1. some
2. numbers 
3. in 
4. a 
5. list

text can be **bold**, or _italics_, or ~~strikethrough~~

My website is <https://kcrahul1999.github.io/> or [here](https://kcrahul1999.github.io/)

# Section 2: some Math

If you want inline $y = mx + b$

$$
\int_0^1 x^2 dx = \frac{1}{3} \hspace{2em} \beta \hspace{2em} \text{or} \hspace{2em} \hat{\beta}
$$

some latex math:

```{=latex}
\begin{align}
y &= a(b+c) \\
  &= ab + ac
\end{align}
```

# Section 3: code

You can do inline code like so `r format(sqrt(2), digits=3)`

hide the code, show the results
```{r}
#| echo: false

data(mtcars)
cor(mtcars$mpg, mtcars$wt)
```
don't run the code 
```{r}
#| eval: false

data(mtcars)
cor(mtcars$mpg, mtcars$wt)
```
# Section 4: plots
```{r}
#| fig-height: 2
#| fig-width: 2
#| fig-align: center

mtcars |>
    ggplot(aes(mpg, wt)) +
    geom_point(col="dodgerblue4", size=2)
```

#Section 5: Tables
```{r}
mtcars[1:5, ]
```

```{r}
knitr::kable(mtcars[1:5, ], )
```

# Bonus Section

:::{.callout-note collapse="true"}
## note title

```{r}
#| echo: false

p <- mtcars |>
    ggplot(aes(mpg, wt)) +
    geom_point(col="dodgerblue4", size=2)
print(p)
```

:::


a tabset panel

:::{.panel-tabset}

## tab1
```{r}
#| echo: false

p
```

## tab2

```{r}
#| echo: false
#| message: false

p + geom_smooth(method="lm", se=F)
```

:::

